Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-09-02 Journal1/paper5TNSM/pr.tex
add paper for revised

In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN. As shown in Fig. \ref{fig:c11}, O-RU is a logical node that contains RF and low PHY. The former transmits or receives radio signals, while the latter includes digital beamforming. Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC. It contains a subfunction of the eNodeB and is deployed near the O-RU.
Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
Moreover, O-CU-UP is connected to user plane function (UPF) via O-backhaul link.
The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. Orchestration and Automation include functions such as RIC Non-Real-Time. RIC is responsible for machine learning methods and making the system more intelligent.
\textcolor{MidnightBlue}{Furthermore, as shown in Fig \ref{fig:c11},  some O-RAN components, such as UPF, O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs.}
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
%\begin{table}[H]
% \caption {List OF Notation} \label{table:1a}
% \begin{center}
% \scalebox{0.8}{
%  \begin{tabular}{||c | c ||}
%  \hline
%Notation & Description \\ [0.5ex]
%  \hline\hline
%  $S$ & Total number of slices\\
%  \hline
%  $S1$ & Number of eMBB slices  \\
%  \hline
% $S2$ & Number of URLLC slices  \\
%  \hline
%  $S3$ & Number of mMTC slices \\
%  \hline
%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
%  \hline
%  PRB &  Physical Resource Block \\
%  \hline
%  eMBB & enhanced Mobile BroadBand \\
%  \hline
%  URLLC  & Ultra-Reliable Low Latency Communication \\
%   \hline
%  mMTC &  massive Machine-To-Machine Communications \\
%  \hline
%  O-RU &  O-RAN Radio Unit \\
%  \hline
%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
%  \hline
%   O-CU &  O-RAN Central Unit \\ [.5ex]
%  \hline
%  UPF &  User Plane Function \\ [.5ex]
%  \hline
% \end{tabular}}
% \end{center}
% \end{table}
\section{System Model}\label{systemmodel}
We consider a downlink (DL) system, and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
In this section, we present the system and signal model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system. Moreover, we discuss the mean delay and the power of VNFs.
\subsection{System Model}
Assume, there are three service types: eMBB, URLLC, and mMTC, which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S = S_1 + S_2 + S_3$ pre-allocated slices serving these services.
Moreover, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have the set
$\{1,2,...,S_1\}$ of eMBB service instances, the set $\{1,2,...,S_2\}$ of URLLC service instances, and the set
$\{1,2,...,S_3\}$ of mMTC service instances.
Each service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
Based on the application and QoS request, UE may be admitted and allocated to the resources.

>>>>

In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN. As shown in Fig. \ref{fig:c11}, O-RU is a logical node that contains RF and low PHY. The former transmits or receives radio signals, while the latter includes digital beamforming. Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC. It contains a subfunction of the eNodeB and is deployed near the O-RU.
Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
Moreover, O-CU-UP is connected to user plane function (UPF) via O-backhaul link.
The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. Orchestration and Automation include functions such as RIC Non-Real-Time. RIC is responsible for machine learning methods and making the system more intelligent.
\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV). Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.
As a result, some O-RAN components such as user plane function (UPF), O-CU, O-DU, and RIC-near real-time, are virtualized and implemented as VNFs.}
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
%\begin{table}[H]
% \caption {List OF Notation} \label{table:1a}
% \begin{center}
% \scalebox{0.8}{
%  \begin{tabular}{||c | c ||}
%  \hline
%Notation & Description \\ [0.5ex]
%  \hline\hline
%  $S$ & Total number of slices\\
%  \hline
%  $S1$ & Number of eMBB slices  \\
%  \hline
% $S2$ & Number of URLLC slices  \\
%  \hline
%  $S3$ & Number of mMTC slices \\
%  \hline
%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
%  \hline
%  PRB &  Physical Resource Block \\
%  \hline
%  eMBB & enhanced Mobile BroadBand \\
%  \hline
%  URLLC  & Ultra-Reliable Low Latency Communication \\
%   \hline
%  mMTC &  massive Machine-To-Machine Communications \\
%  \hline
%  O-RU &  O-RAN Radio Unit \\
%  \hline
%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
%  \hline
%   O-CU &  O-RAN Central Unit \\ [.5ex]
%  \hline
%  UPF &  User Plane Function \\ [.5ex]
%  \hline
% \end{tabular}}
% \end{center}
% \end{table}
\section{System Model}\label{systemmodel}
We consider a downlink (DL) system, and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
In this section, we present the system and signal model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system. Moreover, we discuss the mean delay and the power of VNFs.
\subsection{System Model}
Assume, there are three service types: eMBB, URLLC, and mMTC, which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S = S_1 + S_2 + S_3$ pre-allocated slices serving these services.
Moreover, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have the set
$\{1,2,...,S_1\}$ of eMBB service instances, the set $\{1,2,...,S_2\}$ of URLLC service instances, and the set
$\{1,2,...,S_3\}$ of mMTC service instances.
Each service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
Based on the application and QoS request, UE may be admitted and allocated to the resources.
